The Astropy Project

### 2017-10-31 main.tex
remove whitespace

As of version 2.0, \astropypkg contains $212244$ lines of code \footnote{This line count includes comments, as these are often as important for maintainability as the code itself.  Without comments there are $142197$ lines of code} contributed by $232$ unique
contributors over $19270$ \texttt{git} commits.
The commit distribution follows an approximate power-law (with log-slope of $\sim -0.47$), meaning most of the commits were and are contributed by a relatively small fraction of the contributor pool. $\sim 50$ percent of the commits were contributed by the top $4$ contributors, while $\sim 90$ percent of the commits came from the top $24$.

>>>>

As of version 2.0, \astropypkg contains $212244$ lines of code\footnote{This line count includes comments, as these are often as important for maintainability as the code itself.  Without comments there are $142197$ lines of code} contributed by $232$ unique
contributors over $19270$ \texttt{git} commits.
The commit distribution follows an approximate power-law (with log-slope of $\sim -0.47$), meaning most of the commits were and are contributed by a relatively small fraction of the contributor pool. $\sim 50$ percent of the commits were contributed by the top $4$ contributors, while $\sim 90$ percent of the commits came from the top $24$.
